EDA - Coupons
========================================================

```{r options, echo=FALSE, warning=FALSE, results='hide',message=FALSE}
library(plyr)
library(knitr)
library(ggplot2)
opts_chunk$set(cache=TRUE, autodep=TRUE, echo=T, warning=FALSE, message=FALSE)
#setwd("Code")
```

Coupon List
------------
The coupon list is the list of coupons offered.  In the ER diagram it is called the 'Coupon Master'.

```{r load list}
CLtrain <- read.csv("../Data/coupon_list_train.csv", stringsAsFactors=F)
CLtest <- read.csv("../Data/coupon_list_test.csv", stringsAsFactors=F)


CLtrain$DISPFROM <- as.Date(CLtrain$DISPFROM)
CLtrain$DISPEND <- as.Date(CLtrain$DISPEND)
CLtrain$VALIDFROM <- as.Date(CLtrain$VALIDFROM)
CLtrain$VALIDEND <- as.Date(CLtrain$VALIDEND)

summary(CLtrain)
head(CLtrain)
str(CLtrain)
str(CLtest)
```

So some observations:  There are three geographies involved 
* where is the shop where the deal is offered located 
* where the user lives
* the distribution of the deal  

```{r compare}
CLtest$COUPON_ID_HASH %in% CLtrain$COUPON_ID_HASH
CLtrain$COUPON_ID_HASH %in% CLtest$COUPON_ID_HASH
```

We can translate the groups by the frequency order...

Here we join them onto the data set.  the last table calculates the test set of coupons for reference and also to help us identify what genres don't require predictions and the categories that we will need to do the most predictions for. 

```{r capsule}
capsule <- read.csv("../Data/capsule.csv")
cap <- table(CLtrain$CAPSULE_TEXT)
cap[grep("^WEB",names(cap))]<- 43
cap <- sort(cap, decreasing=T)
capsule <- cbind(capsule, names(cap), cap)
caps <- capsule[,c(2,3)]
names(caps)<- c("Eng","CAPSULE_TEXT")
CLtrain <- merge(CLtrain, caps, by="CAPSULE_TEXT")
head(CLtrain)
caps[caps$Eng=="Spa",]
rownames(capsule) <- capsule$English.Translation
names(capsule$cap) <- capsule$English.Translation
capsule$CAPSULE_TEXT-capsule$cap
sum(capsule$CAPSULE_TEXT-capsule$cap)
```



Descriptive statistics & quality check
------------ 

Each row is a unique coupon
```{r uniques}
length(CLtrain$COUPON_ID_hash)-length(unique(CLtrain$COUPON_ID_hash))
```

High Incidence of Delivery and Food deals, then hotels and spas 

```{r deal frequency, fig.width=8, fig.height=7}
ggplot(CLtrain)+geom_bar(aes(x=Eng))+ggtitle("distribution of Coupons by Capsule Text")+
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0))

```
str(CLtrain)
here is the distribution of prices 

```{r face value pricing, fig.width=8, fig.height=7}
ggplot(CLtrain)+geom_boxplot(aes(x=Eng, y=CATALOG_PRICE))+ggtitle("Face Value price ranges by Capsule")+
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0))+
  coord_cartesian(ylim = c(0, 200000))
```

Discount ranges vary greatly.  Across majority of the categories discount is at least 50%.

```{r discount depth, fig.width=8, fig.height=7}
ggplot(CLtrain)+geom_boxplot(aes(x=Eng, y=PRICE_RATE))+ggtitle("Discount Depth ranges by Capsule")+
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0))
#  coord_cartesian(ylim = c(0, 200000))
```

Summarizing medians into a table

```{r summary}
ddply(CLtrain, .(Eng), summarize, 
      TotalDeals = length(Eng),
      medianFace = median(CATALOG_PRICE),
      medianDiscount= median(PRICE_RATE),
      medianOffered = median(DISCOUNT_PRICE))
```

### Exploring Days of Week offered
A data feature is that there are NAs in the days of the week that are usable for coupons that don't have a usable date - i.e. delivery services.  We can group genres that have important restrictions on dates and which don't...

Weekday Categories are impacted by the days of the week.  No Day Categories don't have day restrictions... they don't make sense.

```{r }
NAtab <- table(is.na(CLtrain$USABLE_DATE_MON),CLtrain$Eng)
pNAtab <- prop.table(NAtab,2)
WeekdayCats <- names(which(pNAtab[2,]<0.1))
NoDayCats <- names(which(pNAtab[2,]>0.1))
WeekdayCats
NoDayCats
```

